---
title: Mock Title
subtitle: Mock Subtitle
author: Mock Author
date: "1970-01-01"
abstract: |

  #### Whatever wolf umami farm-to-table

  The node on the stalk of wheat grew daily. Leaves turn brown and yellow in the
  fall. Feel the heat of the weak dying flame.

  #### Portland bitters Brooklyn mustache

  The night shift men rate extra pay. In some forin or other we need fun. The
  red paper brightened the dim stage. Take the match and strike it against your
  shoe.

execute:
  echo: false
  message: false
  warning: false
  error: false

format:
  html: default
  epub: default
  gfm:
    output-ext: txt
    execute:
      eval: false
      output: false
---

# Basic Markdown

## Headings B--F

A thin book fits in the side pocket. Greet the new guests and leave quickly. The
pirates seized the crew of the lost ship. The show was a flop from the very
start. The first worm gets snapped early. The box is held by a bright red
snapper. It is a band of steel three inches wide. The old pan was covered with
hard fudge. The sofa cushion is red and of light weight. Oats are a food eaten
by horse and man. Boards will warp unless kept dry.

Serve the hot rum to the tired heroes. They floated on the raft to sun their
white backs. No cement will hold hard wood. Mud was spattered on the front of
his white shirt. A tame squirrel makes a nice pet. She danced like a swan, tall
and graceful.

### Heading C: Authentic lomo

The ramp led up to the wide highway. Bail the boat, to stop it from sinking. The
key you designed will fit the lock. The map had an X that meant nothing. There
the flood mark is ten inches. The square peg will settle in the round hole. We
need an end of all such matter. The young kid jumped the rusty gate.

#### Heading D: Kale chips

A white silk jacket goes with any shoes. The ink stain dried on the finished
page. Many hands help get the job done. Thieves who rob friends deserve jail.
The spot on the blotter was made by green ink. A thing of small note can cause
despair. Pluck the bright rose without leaves. When the frost has come it is
time for turkey. Bathe and relax in the cool green grass. A man in a blue
sweater sat at the desk.

##### Heading E: Art party

He used the lathe to make brass objects. Kick the ball straight and follow
through. The key you designed will fit the lock. The music played on while they
talked. Lush fern grow on the lofty rocks. Our troops are set to strike heavy
blows. Pluck the bright rose without leaves. We are sure that one war is enough.
A whiff of it will cure the most stubborn cold. Dip the pail once and let it
settle. The big red apple fell to the ground.

###### Heading F: Cray direct trade

The crunch of feet in the snow was the only sound. A king ruled the state in the
early days. The fight will end in just six minutes. Loop the braid to the left
and then over. What joy there is in living.

## Inline formatting and links

|                  |                            |                          |
|:-----------------|:--------------------------:|:------------------------:|
| Pandoc ligatures |  `--, ---, ..., 'x', "x"`  |  --, ---, ..., 'x', "x"  |
| common ligatures |   `ff, fi, fl, ffi, ffl`   |   ff, fi, fl, ffi, ffl   |
| emphasis         |    `*emphasized text*`     |    *emphasized text*     |
| strong           |     `**strong text**`      |     **strong text**      |
| strikeout        |    `~~strikeout text~~`    |    ~~strikeout text~~    |
| subscript        |          `H~2~O`           |          H~2~O           |
| superscript      |          `2^10^`           |          2^10^           |
| verbatim         |   `` `verbatim text` ``    |     `verbatim text`      |
| math             |      `$e^{i\pi}=-1$`       |      $e^{i\pi}=-1$       |
| small caps       | `[small caps]{.smallcaps}` | [small caps]{.smallcaps} |

## Math

$$
E = mc^{2}
$$

## Block quotations

> The fur of cats goes by many names. The pencil was cut to be sharp at both
> ends. The wagon moved on well oiled wheels. The store was jammed before the
> sale could start.
>
> The hinge on the door creaked with old age. Madam, this is the best brand of
> corn. The brown house was on fire to the attic. The vast space stretched into
> the far distance. Send the stuff in a thick paper bag.

## Line blocks

| The limerick packs laughs anatomical
| Into space that is quite economical.
|     But the good ones I've seen
|     So seldom are clean
| And the clean ones so seldom are comical.

## Lists

### Unordered lists

#### Compact

-   One
-   Two
-   Three

#### Loose

-   Sever the twine with a quick snip of the knife. That guy is the writer of a
    few banned books. The youth drove with zest, but little skill. The hostess
    taught the new maid to serve. The odor of spring makes young hearts jump.

-   The hog crawled under the high fence. Take the winding path to reach the
    lake. The pipe began to rust while new. The desk was firm on the shaky
    floor. Roads are paved with sticky tar. Move the vat over the hot fire. The
    box was thrown beside the parked truck. The bunch of grapes was pressed into
    wine. The pencils have all been used. It caught its hind paw in a rusty
    trap. They felt gay when the ship arrived in port.

-   There are many ways to do these things. Peep under the tent and see the
    clowns. A brown leather bag hung from its strap. Feel the heat of the weak
    dying flame. Code is used when secrets are sent. Down that road is the way
    to the grain farmer. The rarest spice comes from the far East. The logs fell
    and tumbled into the clear stream. The key you designed will fit the lock.
    Two blue fish swam in the tank.

### Ordered lists

#### Compact

1.  One
2.  Two
3.  Three

#### Loose

1.  This will lead the world to more sound and fury Glass will clink when struck
    by metal. The wall phone rang loud and often. The best method is to fix it
    in place with clips. Breathe deep and smell the piny air. We now have a new
    base for shipping.

2.  The hogs were fed chopped corn and garbage. Look in the corner to find the
    tan shirt. All sat frozen and watched the screen. The club rented the rink
    for the fifth night. Thick glasses helped him read the print. Breathe deep
    and smell the piny air. The bank pressed for payment of the debt. The steady
    drip is worse than a drenching rain. Crouch before you jump or miss the
    mark. It was a bad error on the part of the new judge. Slidc the tray across
    the glass top. You cannot brew tea in a cold pot.

3.  He sent the figs, but kept the ripe cherries. If you mumble your speech will
    be lost. There is a lag between thought and act. Beat the dust from the rug
    onto the lawn. The sink is the thing in which we pile dishes. The first part
    of the plan needs changing. A chink in the wall allowed a draft to blow.

### Definition lists

Gentrify

:   Kitsch mixtape post-ironic DIY paleo.

Bespoke

:   Kale chips fanny pack you probably haven't heard of them Austin freegan
    Shoreditch, distillery flannel cardigan.

Sriracha

:   Ethnic letterpress cred, Neutra distillery fanny pack kale chips forage
    leggings 8-bit 90's Thundercats.

## Footnotes

For[^1] sale[^2]: baby[^3] shoes[^4], never[^5] worn[^6].

[^1]: Kevin Bacon

[^2]: Lori Singer

[^3]: John Lithgow

[^4]: Dianne Wiest

[^5]: Chris Penn

[^6]: Loose, footloose kick off your Sunday shoes. Please, Louise pull me off a
    my knees. Jack, get back c'mon before we crack. Lose your blues everybody
    cut footloose. Oowhee, Marie shake it, shake it for me. Whoa, Milo c'mon,
    c'mon let's go. Lose your blues everybody cut footloose. Cut footloose. Cut
    footloose. Cut footloose.

## Horizontal rules

--------------------------------------------------------------------------------

## Page break

{{< pagebreak >}}

# Tables

```{r}
#| fig-cap: ...check for tabular numbers too!

head(iris) |>
  knitr::kable()
```

# Figures

```{r}
#| label: fig-charts-r
#| fig-cap: Charts
#| fig-subcap:
#|   - "Cars"
#|   - "Pressure"
#| layout-ncol: 2

plot(cars)
plot(pressure)
```

See the [Quarto docs](https://quarto.org/docs/authoring/figures.html) for
fancier examples including advanced figure arrangement.

# Divs

## Custom classes

::: border
This content is styled with the `.border` class.
:::
